Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
changed figure pipeline

In this article, we have propose a full data parallel framework on GPU
hardware which combines an adaptive isosurface construction from
digital data with a curvature tensor estimation at each vertex. Using
this approach, we can explore in real-time different curvature
measurements (mean, Gaussian, principal directions) with different
ball radii on potentially large dynamic dataset. Our proposal relies
on both a linear octree representation with Morton codes and an
efficient integral computation on GPU. The source code and additional
material (video, \ldots) are available on the project website
(\url{https://github.com/dcoeurjo/ICTV}).

An extension of this framework could be to implement an approximate hierarchical
algorithm. From there, we could use the dynamic refinement scheme to compute
the curvature with the hierarchical algorithm, thus massively reducing the number of probes.
We could also use trexture streaming to compute on the fly on the CPU the subdivision and
stream it to the GPU, allowing dynamic radii change with the hierarchical algorithm.
This framework could also be used for feature detection purposes
such as presented in \cite{SMI2015}. The point classification is done by computing
the curvature at different radii and comparing them. Using our framework,
this may be done in a real-time manner.
The computed curvature could finally be used to control the refinement of the
triangulation. We are for now only using the normal computation for shading
purposes but we could imagine using it along with the vertices to do a
Poisson reconstruction of the object.

>>>>

In this article, we have proposed a full data parallel framework on GPU
hardware which combines an adaptive isosurface construction from
digital data with a curvature tensor estimation at each vertex. Using
this approach, we can explore in real-time different curvature
measurements (mean, Gaussian, principal directions) with different
ball radii on potentially large dynamic dataset. Our proposal relies
on both a linear octree representation with Morton codes and an
efficient integral computation on GPU. The source code and additional
material (video, \ldots) are available on the project website
(\url{https://github.com/dcoeurjo/ICTV}).

An extension of this framework could be to implement an approximate hierarchical
algorithm. From there, we could use the dynamic refinement scheme to compute
the curvature with the hierarchical algorithm, thus massively reducing the number of probes.
We could also use trexture streaming to compute on the fly on the CPU the subdivision and
stream it to the GPU, allowing dynamic radii change with the hierarchical algorithm.
Another improvement would be to implement the hierarchical pattern presented Figure~\ref{fig:approx}-$b$.
This would prevent bias addition from adding cells of density 1 but only partly convered by the ball.

This framework could also be used for feature detection purposes
such as presented in \cite{SMI2015}. The point classification is done by computing
the curvature at different radii and comparing them. Using our framework,
this may be done in a real-time manner.
The computed curvature could finally be used to control the refinement of the
triangulation. We are for now only using the normal computation for shading
purposes but we could imagine using it along with the vertices to do a
Poisson reconstruction of the object.
